---
title: "Swiss Covid Wastewater Virus Load Data"
author: Kaspar V.
output:
  html_document:
    df_print: paged
    toc: true
    theme: yeti
    md_extensions: +footnotes
    output_file: docs/index.html
params:
  generate_date: '2023-04-19'
---


```{r libs, echo=FALSE, message=FALSE}
library(rmarkdown)
library(xts)
library(scales)
library(stringr)
library(knitr)
library(tidyverse)
library(shiny)
library(dplyr)

source('lib/load_csv_utils.r')
source('lib/plot_locality.r')

Sys.setenv("VROOM_CONNECTION_SIZE" = 50 * 1024 * 1024)

COVID19Wastewater_vl_website <-
  'https://opendata.swiss/de/dataset/covid-19-schweiz/resource/f8602049-4f86-4f02-a957-10791642283a'
COVID19Wastewater_vl_model <-
  'https://www.covid19.admin.ch/api/data/documentation/models/sources-definitions-wastewaterdailyviralloaddata.md'

COVID19Wastewater_vl_website <-
  'https://opendata.swiss/de/dataset/covid-19-schweiz/resource/f8602049-4f86-4f02-a957-10791642283a'
COVID19Wastewater_vl_model <-
  'https://www.covid19.admin.ch/api/data/documentation/models/sources-definitions-wastewaterdailyviralloaddata.md'

COVID19Cases_geoRegion_w_website <-
  'https://opendata.swiss/de/dataset/covid-19-schweiz/resource/a92be10d-5e2b-4956-9106-cc27bdf44928'
COVID19Cases_geoRegion_w_model <-
  'https://www.covid19.admin.ch/api/data/documentation/models/sources-definitions-weeklyincomingdata.md'

COVID19Cases_geoRegion_AKL10_w_website <-
  'https://opendata.swiss/de/dataset/covid-19-schweiz/resource/fa2ac911-a3da-4193-b21b-70d4e9b3f0fe'
COVID19Cases_geoRegion_AKL10_w_model <-
  'https://www.covid19.admin.ch/api/data/documentation/models/sources-definitions-weeklyincomingdata.md'

COVID19Test_geoRegion_w_website <-
  'https://opendata.swiss/de/dataset/covid-19-schweiz/resource/eaa0b68f-a269-4bb6-9d0d-0a9492f4639c'
COVID19Test_geoRegion_w_model <-
  'https://www.covid19.admin.ch/api/data/documentation/models/sources-definitions-weeklyincomingdata.md'

COVID19Death_geoRegion_w_website <-
  'https://opendata.swiss/de/dataset/covid-19-schweiz/resource/c9af140c-793a-4d91-bf75-121fee2440ae'
COVID19Death_geoRegion_w_model <-
  'https://www.covid19.admin.ch/api/data/documentation/models/sources-definitions-weeklyincomingdata.md'

```

```{r load_data, echo=FALSE, message=FALSE}

# COVID19Wastewater_vl_csv <- 'data/COVID19Wastewater_vl.csv'
COVID19Wastewater_vl_csv <- get_csv_url(COVID19Wastewater_vl_website)

# COVID19Wastewater_vl <- load_COVID19Wastewater_vl(COVID19Wastewater_vl_csv)
# localities <- get_localities(COVID19Wastewater_vl)

# COVID19Cases_geoRegion_w <- get_COVID19Cases_geoRegion_w(COVID19Cases_geoRegion_w_website)

# COVID19Death_geoRegion_w <- get_COVID19Death_geoRegion_w(COVID19Death_geoRegion_w_website)
# COVID19Cases_geoRegion_AKL10_w <- get_COVID19Cases_geoRegion_AKL10_w(COVID19Cases_geoRegion_AKL10_w_website)

```


```{r, echo=FALSE, message=FALSE}
plot_locality = function(geoRegion, name, canton, population) {
  locality_data <- get_locality_data(COVID19Wastewater_vl, geoRegion)
  plot_main <- str_interp("${name} ${canton} – ${population} P.")
  render_locality_plot(locality_data, plot_main)
}
```

## Information

This document is a personal throw together to get some personal insight into the COVID-19 wastewater virus load data.  
The original data was published by the Swiss Federal Office of Public Health.

- [Covid-⁠19 – Viruslast im Abwasser – Bundesamt für Gesundheit BAG](https://www.covid19.admin.ch/de/epidemiologic/waste-water)
- [Data source website - opendata.swiss](`r COVID19Wastewater_vl_website`)  
- [Data model documentation](`r COVID19Wastewater_vl_model`)
- [Source document (CSV ~5.5MB)](`r COVID19Wastewater_vl_csv`)
- [Source of this document (R Markdown)](https://github.com/casaper/swiss_wastewater_covid_virus_load/blob/main/wastewater.Rmd)
- Generated at `r params$generate_date`

## Wastewater Localities

### Werdhölzli ZH – 471'000 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(26101, 'Werdhölzli', 'ZH', 471000)
```

### Aire GE – 451'771 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(664301, 'Aire', 'GE', 451771)
```

### Basel BS – 273'075 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(270101, 'Basel', 'BS', 273075)
```

### Lausanne (Vidy) VD – 247'824 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(558600, 'Lausanne (Vidy)', 'VD', 247824)
```

### Region Bern BE – 224'557 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(35100, 'Region Bern', 'BE', 224557)
```

### Buholz (Real) LU – 183'511 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(102400, 'Buholz (Real)', 'LU', 183511)
```

### Cham (Schoenau) ZG – 146'942 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(170200, 'Cham (Schoenau)', 'ZG', 146942)
```

### Winterthur ZH – 140'403 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(23001, 'Winterthur', 'ZH', 140403)
```

### Thunersee BE – 124'550 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(94400, 'Thunersee', 'BE', 124550)
```

### Lugano TI – 124'000 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(515100, 'Lugano', 'TI', 124000)
```

### Ramsen (Bibertal-Hegau) SH – 100'338 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(296300, 'Ramsen (Bibertal-Hegau)', 'SH', 100338)
```

### Zuchwil (Soloth.-Emme) SO – 95'793 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(253400, 'Zuchwil (Soloth.-Emme)', 'SO', 95793)
```

### Biel BE – 85'389 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(73300, 'Biel', 'BE', 85389)
```

### Dietikon (Limeco) ZH – 83'367 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(24301, 'Dietikon (Limeco)', 'ZH', 83367)
```

### Birs BL – 83'312 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(276600, 'Birs', 'BL', 83312)
```

### Satigny/Bois-de-Bay GE – 79'577 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(663801, 'Satigny/Bois-de-Bay', 'GE', 79577)
```

### Aarau AG – 78'255 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(400100, 'Aarau', 'AG', 78255)
```

### Worblental BE – 71'636 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(36200, 'Worblental', 'BE', 71636)
```

### Altenrhein SG – 64'000 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(323700, 'Altenrhein', 'SG', 64000)
```

### Laupen BE – 62'000 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(66700, 'Laupen', 'BE', 62000)
```

### Baden AG – 59'560 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(404200, 'Baden', 'AG', 59560)
```

### St.Gallen (Hofen) SG – 57'031 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(320401, 'St.Gallen (Hofen)', 'SG', 57031)
```

### Neuhausen A/Rhf. (Roeti) SH – 56'967 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(293700, 'Neuhausen A/Rhf. (Roeti)', 'SH', 56967)
```

### Chur GR – 55'000 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(390101, 'Chur', 'GR', 55000)
```

### Lenzburg AG – 54'568 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(420300, 'Lenzburg', 'AG', 54568)
```

### Winznau (Zv Olten) SO – 54'540 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(250100, 'Winznau (Zv Olten)', 'SO', 54540)
```

### Vevey (Aviron) VD – 53'864 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(589000, 'Vevey (Aviron)', 'VD', 53864)
```

### Bellinzona (Giubiasco) TI – 53'209 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(500200, 'Bellinzona (Giubiasco)', 'TI', 53209)
```

### Thonex/Villette GE – 51'028 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(664000, 'Thonex/Villette', 'GE', 51028)
```

### Locarno (Foce Maggia) TI – 50'781 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(511302, 'Locarno (Foce Maggia)', 'TI', 50781)
```

### Glarnerland GL – 49'644 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(160200, 'Glarnerland', 'GL', 49644)
```

### Grenchen (Buerenamt) SO – 46'563 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(254600, 'Grenchen (Buerenamt)', 'SO', 46563)
```

### Brugg AG – 46'250 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(412300, 'Brugg', 'AG', 46250)
```

### Fribourg (Aele) FR – 44'211 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(219600, 'Fribourg (Aele)', 'FR', 44211)
```

### Niederglatt (Fischb.-Gl.) ZH – 43'596 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(8901, 'Niederglatt (Fischb.-Gl.)', 'ZH', 43596)
```

### Montreux/Pierrier VD – 41'383 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(588600, 'Montreux/Pierrier', 'VD', 41383)
```

### Uster (Jungholz) ZH – 41'303 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(19801, 'Uster (Jungholz)', 'ZH', 41303)
```

### Au (Rosenbergsau) SG – 41'281 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(323100, 'Au (Rosenbergsau)', 'SG', 41281)
```

### Aarwangen (Zala) BE – 40'845 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(32101, 'Aarwangen (Zala)', 'BE', 40845)
```

### Neuchatel NE – 40'697 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(645800, 'Neuchatel', 'NE', 40697)
```

### Martigny VS – 39'643 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(613600, 'Martigny', 'VS', 39643)
```

### Dübendorf (Ika Neugut) ZH – 39'622 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(19101, 'Dübendorf (Ika Neugut)', 'ZH', 39622)
```

### 000', 'Liechtenstein FL – 39'315 Population

```{r, echo=FALSE, message=FALSE}
plot_locality('100000', 'Liechtenstein', 'FL', 39315)
```

### Morges VD – 39'126 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(564200, 'Morges', 'VD', 39126)
```

### St.Gallen (Au) SG – 37'876 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(320302, 'St.Gallen (Au)', 'SG', 37876)
```

### Ergolz 2 BL – 37'565 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(282500, 'Ergolz 2', 'BL', 37565)
```

### Delemont (Sede) JU – 36'484 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(670900, 'Delemont (Sede)', 'JU', 36484)
```

### Burgdorf BE – 36'465 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(40100, 'Burgdorf', 'BE', 36465)
```

### Frauenfeld TG – 36'369 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(456600, 'Frauenfeld', 'TG', 36369)
```

### Lyss BE – 36'358 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(30600, 'Lyss', 'BE', 36358)
```

### Gland (Apec) VD – 36'034 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(572100, 'Gland (Apec)', 'VD', 36034)
```

### Sion/Chateauneuf VS – 35'632 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(626601, 'Sion/Chateauneuf', 'VS', 35632)
```

### Bülach ZH – 35'612 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(5301, 'Bülach', 'ZH', 35612)
```

### Zofingen AG – 35'577 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(428000, 'Zofingen', 'AG', 35577)
```

### Yverdon VD – 35'462 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(593800, 'Yverdon', 'VD', 35462)
```

### La-Chaux-de-Fonds NE – 35'360 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(642100, 'La-Chaux-de-Fonds', 'NE', 35360)
```

### Vuippens (Ais) FR – 34'647 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(216100, 'Vuippens (Ais)', 'FR', 34647)
```

### Altdorf UR – 33'940 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(120101, 'Altdorf', 'UR', 33940)
```

### Moossee-Urtenenbach BE – 33'844 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(41100, 'Moossee-Urtenenbach', 'BE', 33844)
```

### Sierre/Noes VS – 32'480 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(624801, 'Sierre/Noes', 'VS', 32480)
```

### Wohlen AG – 31'992 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(408200, 'Wohlen', 'AG', 31992)
```

### Wetzikon (Flos) ZH – 31'419 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(12101, 'Wetzikon (Flos)', 'ZH', 31419)
```

### Weinfelden (Mittelthurgau) TG – 31'342 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(494600, 'Weinfelden (Mittelthurgau)', 'TG', 31342)
```

### Schwyz SZ – 31'164 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(137200, 'Schwyz', 'SZ', 31164)
```

### Aarburg AG – 30'884 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(427100, 'Aarburg', 'AG', 30884)
```

### Steinach (Morgental) SG – 30'710 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(321700, 'Steinach (Morgental)', 'SG', 30710)
```

### Alpnach (Sarneraatal) OW – 30'657 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(140100, 'Alpnach (Sarneraatal)', 'OW', 30657)
```

### Flawil (Oberglatt) SG – 30'378 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(340200, 'Flawil (Oberglatt)', 'SG', 30378)
```

### Affoltern am Albis ZH – 30'226 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(201, 'Affoltern am Albis', 'ZH', 30226)
```

### Hoefe SZ – 29'624 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(132200, 'Hoefe', 'SZ', 29624)
```

### Untermarch SZ – 29'470 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(134400, 'Untermarch', 'SZ', 29470)
```

### Mendrisio (Rancate) TI – 29'392 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(526200, 'Mendrisio (Rancate)', 'TI', 29392)
```

### Ergolz 1 BL – 29'168 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(286100, 'Ergolz 1', 'BL', 29168)
```

### Rontal LU – 28'771 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(106500, 'Rontal', 'LU', 28771)
```

### Brig-Glis (Briglina) VS – 28'678 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(600200, 'Brig-Glis (Briglina)', 'VS', 28678)
```

### Rapperswil-Jona SG – 28'168 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(333500, 'Rapperswil-Jona', 'SG', 28168)
```

### Interlaken BE – 27'945 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(59300, 'Interlaken', 'BE', 27945)
```

### Colombier (La Saunerie) NE – 27'582 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(640600, 'Colombier (La Saunerie)', 'NE', 27582)
```

### Horgen ZH – 26'952 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(13301, 'Horgen', 'ZH', 26952)
```

### Chiasso (Vacallo) TI – 26'638 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(526800, 'Chiasso (Vacallo)', 'TI', 26638)
```

### Meilen (Rorguet) ZH – 26'447 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(15601, 'Meilen (Rorguet)', 'ZH', 26447)
```

### Wil SG – 26'295 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(342500, 'Wil', 'SG', 26295)
```

### Pratteln/Rhein BL – 26'286 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(283100, 'Pratteln/Rhein', 'BL', 26286)
```

### Nyon VD – 25'753 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(572400, 'Nyon', 'VD', 25753)
```

### Mittl. Emmental BE – 25'733 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(95600, 'Mittl. Emmental', 'BE', 25733)
```

### Kaisten AG – 25'354 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(416900, 'Kaisten', 'AG', 25354)
```

### Birsig BL – 24'943 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(277500, 'Birsig', 'BL', 24943)
```

### Buchs SG – 24'844 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(327100, 'Buchs', 'SG', 24844)
```

### Locarno (Foce Ticino) TI – 24'516 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(511301, 'Locarno (Foce Ticino)', 'TI', 24516)
```

### Zwingen (Laufental-L-Tal) BL – 24'357 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(279300, 'Zwingen (Laufental-L-Tal)', 'BL', 24357)
```

### Reinach AG – 23'817 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(414100, 'Reinach', 'AG', 23817)
```

### Hefenhofen (Aachtal, Moos) TG – 23'074 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(441600, 'Hefenhofen (Aachtal, Moos)', 'TG', 23074)
```

### Bremgarten AG – 22'613 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(406300, 'Bremgarten', 'AG', 22613)
```

### Commugny VD – 22'575 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(571100, 'Commugny', 'VD', 22575)
```

### Stans (Rotzwinkel) NW – 21'214 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(150900, 'Stans (Rotzwinkel)', 'NW', 21214)
```

### Illnau-Effretikon ZH – 18'921 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(17401, 'Illnau-Effretikon', 'ZH', 18921)
```

### Landquart GR – 17'054 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(395501, 'Landquart', 'GR', 17054)
```

### Herisau (Bachwis) AR – 16'500 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(300102, 'Herisau (Bachwis)', 'AR', 16500)
```

### Porrentruy (Sepe) JU – 16'500 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(680000, 'Porrentruy (Sepe)', 'JU', 16500)
```

### S-chanf (Oberengadin) GR – 15'056 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(378802, 'S-chanf (Oberengadin)', 'GR', 15056)
```

### Hallau (Klettgau) SH – 14'795 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(297100, 'Hallau (Klettgau)', 'SH', 14795)
```

### Flums (Seez) SG – 12'448 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(329200, 'Flums (Seez)', 'SG', 12448)
```

### Bad Ragaz SG – 12'007 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(329100, 'Bad Ragaz', 'SG', 12007)
```

### Appenzell (Boedeli) AI – 11'877 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(310100, 'Appenzell (Boedeli)', 'AI', 11877)
```

### Cazis (Waldau) GR – 10'963 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(366101, 'Cazis (Waldau)', 'GR', 10963)
```

### Davos (Gadenstatt) GR – 9'706 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(385102, 'Davos (Gadenstatt)', 'GR', 9706)
```

### Saanen BE – 9'253 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(84300, 'Saanen', 'BE', 9253)
```

### Seewis (Vorderes Prättigau) GR – 8'003 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(397201, 'Seewis (Vorderes Prättigau)', 'GR', 8003)
```

### Schluein (Gruob) GR – 7'823 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(358201, 'Schluein (Gruob)', 'GR', 7823)
```

### Bagnes-Le Châble VS – 7'713 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(603102, 'Bagnes-Le Châble', 'VS', 7713)
```

### Andelfingen ZH – 7'150 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(3001, 'Andelfingen', 'ZH', 7150)
```

### Zermatt VS – 5'507 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(630000, 'Zermatt', 'VS', 5507)
```

### Goms VS – 4'193 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(605700, 'Goms', 'VS', 4193)
```

### Grindelwald BE – 4'153 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(57600, 'Grindelwald', 'BE', 4153)
```

### Engelberg OW – 4'053 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(140200, 'Engelberg', 'OW', 4053)
```

### Scuol (Sot Ruinas) GR – 3'473 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(376201, 'Scuol (Sot Ruinas)', 'GR', 3473)
```

### Poschiavo (Li Geri) GR – 3'358 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(356101, 'Poschiavo (Li Geri)', 'GR', 3358)
```

### Klosters (Gulfia) GR – 3'155 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(387101, 'Klosters (Gulfia)', 'GR', 3155)
```

### Lauterbrunnen BE – 2'553 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(58400, 'Lauterbrunnen', 'BE', 2553)
```

### Arosa GR – 2'049 Population

```{r, echo=FALSE, message=FALSE}
plot_locality(392101, 'Arosa', 'GR', 2049)
```
